Effects of Trauma Life Support Training Programs on Patient Outcomes: A Pilot Cluster Randomised Trial

### 2024-09-28 pilot-publication/manuscript.Rmd
Work on creating a new consort style diagram

>>>>

```{dot}
digraph consort {

  # Node attributes
  node [shape=square, fontname=Helvetica, fontsize=10]

  # Define nodes
  A [label='Total: Clusters: 30 | Residents: 90 | Patients: 270']
  B [label='Standard Care\nClusters: 10\nResidents: 30\nPatients: 90']
  C [label='ATLS\nClusters: 10\nResidents: 30\nPatients: 90']
  D [label='PTC\nClusters: 10\nResidents: 30\nPatients: 90']

  # Define mid-point node to facilitate splitting
  mid [shape=point, width=0, label='']

  # Edges
  A -> mid [arrowhead=none]  # Line from A to mid-point without arrowhead
  mid -> B [tailport=s, headport=n]  # Line from mid to Standard Care
  mid -> C [tailport=s, headport=n]  # Line from mid to ATLS
  mid -> D [tailport=s, headport=n]  # Line from mid to PTC
}
```
